### 2018-06-30 paper/2-background.tex
Work on S2-S3, add a figure with key abstractions

\begin{figure}
\vspace{-2mm}
\centerline{\includegraphics[scale=0.28]{fig/shake-example-cutoff.pdf}}
\vspace{-3mm}
\caption{An early cutoff example: if a comment is added to \cmd{main.c}, the
rebuild is stopped after detecting that \cmd{main.o} is unchanged, since this
indicates that \cmd{main.exe} and its dependents do not need to be
rebuilt.\label{fig-cutoff}}
\vspace{-4mm}
\end{figure}

@@

\subsection{\Bazel: a cloud build system}
\label{sec-background-bazel}

When build systems are used by large teams, different team members often end up
executing exactly the same tasks on their local machines. A \emph{cloud build
system} can speed up builds dramatically by sharing build results
among team members. Furthermore, cloud build systems allow one to perform
\emph{shallow builds} that materialise only end build products locally, leaving
all intermediates in the cloud. We illustrate shallow cloud builds by an example
in Fig.~\ref{fig-bazel}.

The user starts by downloading the project sources, whose content hashes are
(for simplicity)~1,~2 and~3, and requests to build \cmd{main.exe}, see
Fig.~\ref{fig-bazel}(a,b). By looking up the global history of all previous
builds of the project\footnote{Here we ignore the issue of limited cloud storage
resources for the sake of simplicity; in practice, old entries are regularly
evicted from the storage, as further discussed in~\S\ref{sec-cloud-aspects}.},
the build system finds that someone has already compiled these exact sources
before and the resulting files \cmd{util.o} and \cmd{main.o} had hashes
4~and~5, respectively. Similarly, the build system finds that the hash of the
resulting \cmd{main.exe} was 6 and downloads the actual binary from the shared
cloud storage -- it must be materialised, because it is the end build product.

In the second scenario, shown in Fig.~\ref{fig-bazel}(c), the user modifies the
source file \cmd{util.c}, thereby changing its hash from~1~to~7. The cloud
lookup of the new combination $\{\cmd{util.c}, \cmd{util.h}\}$ fails,
which means that nobody has ever compiled it. The build system must therefore
build \cmd{util.o}, which results in materialising it with a new hash~8. The
combination of hashes of \cmd{util.o} and \cmd{main.o} has not been encountered
before either, therefore the build system first downloads \cmd{main.o} from the
cloud and then builds \cmd{main.exe} by linking the two object files. When the
build is complete, the results can be uploaded to the cloud for future reuse by
other team members.

@@

To support cloud builds, \Bazel maintains (i) a \emph{content-addressable cache}
that can be used to download a previously built file given the hash of its
content, and (ii) the history of all executed build commands annotated with
observed file hashes. The latter allows the build engine to bypass the execution
of a task, by predicting the hash of the result from the hashes of its
dependencies, and subsequently download the result from the cache. A concrete
implementation is provided in~\S\ref{sec-implementations}.

\begin{figure}
\begin{subfigure}[b]{0.25\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/bazel-example-checkout.pdf}}
\caption{Download source files}
\end{subfigure}
\begin{subfigure}[b]{0.40\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/bazel-example-build.pdf}}
\caption{Build \cmd{main.exe}}
\end{subfigure}
\begin{subfigure}[b]{0.31\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/bazel-example-rebuild.pdf}}
\caption{Modify \cmd{util.c} and rebuild}
\end{subfigure}
\vspace{-2mm}
\caption{A cloud build example: (a)~download sources, (b)~build \cmd{main.exe}
by downloading it from the cloud and skipping intermediate files (only their
hashes are needed), (c)~modify \cmd{util.c} and rebuild \cmd{main.exe}, which
requires building \cmd{util.o} (nobody has compiled \cmd{util.c} before) and
downloading \cmd{main.o} (it is needed for linking \cmd{main.exe}). File hashes
are shown in circles, and non-materialised intermediates in dashed rounded
rectangles.\label{fig-bazel}}
\vspace{-4mm}
\end{figure}

\subsection{Summary}
\label{sec-background-summary}

@@

\begin{table}
\smaller
\centering
\begin{tabular}{l||l|l||l|c|c|c}
\hline
$\!$Build system$\!$& Persistent build information & Scheduler   & Dependencies    & Minimal & Cutoff & Cloud$\!$\\\hline
$\!$\Make       $\!$& File modification times      & Topological & Static          & Yes     & No     & No   $\!$\\
$\!$\Excel      $\!$& Dirty cells, calc chain      & Restarting  & Dynamic         & No      & No     & No   $\!$\\
$\!$\Shake      $\!$& Previous dependency graph    & Suspending  & Dynamic         & Yes     & Yes    & No   $\!$\\
$\!$\Bazel      $\!$& Cloud cache, command history & Restarting  & Dynamic$^{(*)}$ & No      & Yes    & Yes  $\!$\\\hline
\hline
\end{tabular}
\vspace{0.5mm}
\caption{Build system differences; $^{(*)}$at present, user-defined build rules
cannot have dynamic dependencies.\label{tab-summary}}
\vspace{-6mm}
\end{table}

>>>>

\begin{figure}
\vspace{-3mm}
\centerline{\includegraphics[scale=0.28]{fig/shake-example-cutoff.pdf}}
\vspace{-4mm}
\caption{An early cutoff example: if a comment is added to \cmd{main.c}, the
rebuild is stopped after detecting that \cmd{main.o} is unchanged, since this
indicates that \cmd{main.exe} and its dependents do not need to be
rebuilt.\label{fig-cutoff}}
\vspace{-4mm}
\end{figure}

@@

\vspace{-0.5mm}
\subsection{\Bazel: a cloud build system}\label{sec-background-bazel}
\vspace{-0.5mm}

When build systems are used by large teams, different team members often end up
executing exactly the same tasks on their local machines. A \emph{cloud build
system} can speed up builds dramatically by sharing build results
among team members. Furthermore, cloud build systems can support \emph{shallow
builds} that materialise only end build products locally, leaving all
intermediates in the cloud.

Consider an example in Fig.~\ref{fig-bazel}. The user starts by downloading the
sources, whose content hashes are (for simplicity)~1,~2 and~3, and requests to
build \cmd{main.exe}, see Fig.~\ref{fig-bazel}(a,b). By looking up the global
history of all previous builds\footnote{In practice, old entries are regularly
evicted from the cloud storage, as further discussed
in~\S\ref{sec-cloud-aspects}.}, the build system finds that someone has already
compiled these exact sources before and the resulting files \cmd{util.o} and
\cmd{main.o} had hashes 4~and~5, respectively. Similarly, the build system finds
that the hash of the resulting \cmd{main.exe} was 6 and downloads the actual
binary from the cloud storage -- it must be materialised, because it is the end
build product.

In Fig.~\ref{fig-bazel}(c), the user modifies the source file \cmd{util.c},
thereby changing its hash from~1~to~7. The cloud lookup of the new combination
$\{\cmd{util.c}, \cmd{util.h}\}$ fails, which means that nobody has ever
compiled it. The build system must therefore build \cmd{util.o}, materialising
it with the new hash~8. The combination of hashes of \cmd{util.o} and
\cmd{main.o} has not been encountered before either, thus the build system first
downloads \cmd{main.o} from the cloud and then builds \cmd{main.exe} by linking
the two object files. When the build is complete, the results can be uploaded to
the cloud for future reuse by other team members.

@@

To support cloud builds, \Bazel maintains (i) a \emph{content-addressable cache}
that can be used to download a previously built file given the hash of its
content, and (ii) the history of all executed build commands annotated with
observed file hashes. The latter allows the build engine to bypass the execution
of a task, by predicting the hash of the result from the hashes of its
dependencies, and subsequently download the result from the cache. A concrete
implementation is provided in~\S\ref{sec-implementation-cloud}.

\begin{figure}
\vspace{-2mm}
\begin{subfigure}[b]{0.25\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/bazel-example-checkout.pdf}}
\vspace{-1mm}
\caption{Download source files}
\end{subfigure}
\begin{subfigure}[b]{0.40\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/bazel-example-build.pdf}}
\vspace{-1mm}
\caption{Build \cmd{main.exe}}
\end{subfigure}
\begin{subfigure}[b]{0.31\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/bazel-example-rebuild.pdf}}
\vspace{-1mm}
\caption{Modify \cmd{util.c} and rebuild}
\end{subfigure}
\vspace{-2.5mm}
\caption{A cloud build example: (a)~download sources, (b)~build \cmd{main.exe}
by downloading it from the cloud and skipping intermediate files (only their
hashes are needed), (c)~modify \cmd{util.c} and rebuild \cmd{main.exe}, which
requires building \cmd{util.o} (nobody has compiled \cmd{util.c} before) and
downloading \cmd{main.o} (it is needed for linking \cmd{main.exe}). File hashes
are shown in circles, and non-materialised intermediates in dashed rounded
rectangles.\label{fig-bazel}}
\vspace{-3mm}
\end{figure}

\begin{table}[h]
\vspace{-1mm}
\smaller
\centering
\begin{tabular}{l||l|l||l|c|c|c}
\hline
$\!$Build system$\!$& Persistent build information & Scheduler   & Dependencies    & Minimal & Cutoff & Cloud$\!$\\\hline
$\!$\Make       $\!$& File modification times      & Topological & Static          & Yes     & No     & No   $\!$\\
$\!$\Excel      $\!$& Dirty cells, calc chain      & Restarting  & Dynamic         & No      & No     & No   $\!$\\
$\!$\Shake      $\!$& Previous dependency graph    & Suspending  & Dynamic         & Yes     & Yes    & No   $\!$\\
$\!$\Bazel      $\!$& Cloud cache, command history & Restarting  & Dynamic$^{(*)}$ & No      & Yes    & Yes  $\!$\\\hline
\hline
\end{tabular}
\caption{Build system differences; $^{(*)}$at present, user-defined build rules
cannot have dynamic dependencies.\label{tab-summary}}
\vspace{-8mm}
\end{table}

\vspace{-1.5mm}
\subsection{Summary}\label{sec-background-summary}
\vspace{-0.5mm}

@@
